Argennon: A Scalable Smart Contract Platform

### 2022-04-01 tex/sections/elements.tex
Update some parts of `elements.tex`
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

An Argennon application or a smart contract is a collection of method bytecodes and heap chunks that are stored in
the AVM storage, identified by a unique application identifier. An application identifier, \texttt{applicationID}, is
a unique prefix code generated by the \emph{applications} prefix tree. (See Section~\ref{sec:identifiers}.)

An application identifier can
be considered as the address of an application and has the following standard symbolic representation:
\begin{verbatim}
<application-id> ::= <decimal-prefix-code>
<decimal-prefix-code> ::= <dec-num>"."<decimal-prefix-code> | <dec-num>
\end{verbatim}
where \texttt{<dec-num>} is a normal decimal number between $0$ and $255$.

@@

\begin{itemize}
    \item Installation of AVM smart contracts and determining the update policy of a smart
    contract: if the contract is updatable or not, which accounts or smart contracts can update or uninstall
    the contract, and so on.
    \item Removing an AVM smart contract (if allowed).
    \item Updating an AVM smart contract (if allowed).
\end{itemize}

@@

Argennon accounts are entities defined inside the ARG smart contract.
Every Argennon account is uniquely identified by a prefix code generated using \emph{accounts} prefix
tree. (See Section~\ref{sec:identifiers}) An account
identifier can be considered as the address of an account and has the following standard symbolic representation:
\begin{verbatim}
<account-id> ::= <hex-prefix-code>
<hex-prefix-code> ::= "0x"<hex-num>"."<hex-prefix-code> | "0x"<hex-num>
\end{verbatim}
where \texttt{<hex-num>} is a hexadecimal number between $0$ and $255$, using lower case
letters \texttt{[a-f]} for showing digits greater than $9$.

For example \texttt{0x24.0xff.0xda}, \texttt{0x0} and \texttt{0x3.0xa0.0x0.0x0}, are valid standard symbolic
representations of account addresses.

A new account can be created by invoking \texttt{createAccount} method from the Argennon smart contract. For creating
a new account two public keys need to be provided by the caller and registered in the Argennon smart contract.
One public key will be used for issuing digital signatures, and the other one will be used for voting. The
provided public keys need to meet certain cryptographic requirements,\footnote{Argennon uses Prove
Knowledge of the Secret Key (KOSK) scheme.} and can not be already registered in the system.

@@

\section{Transactions}\label{sec:transactions}

@@

\subsection{Resource Declaration}\label{subsec:resource-declaration}

@@

\begin{lstlisting}[language=python, frame=TB, float, title=An Argennon transaction in YAML format,label={lst:txn-example}]
---
fee: |
    PUT /balances/0x73.0xa2?to=fee&amount=0.26&sig=5b73CbmwQNRC7fWUY15 HTTP/1.1
call: |
    POST bttp://dapp.argennon.net/54.189.21/proposals HTTP/1.1
    Content-Type: application/json; charset=utf-8
    Content-Length: 77

>>>>

An Argennon application or smart contract is an HTTP server which is represented by an Argennon Standard
Representation (ASR) and whose state is stored in the Argennon blockchain. Each Argennon application is identified by
a unique application identifier.

An application identifier, \texttt{applicationID}, is
a unique prefix code generated by the \emph{applications} prefix tree. (See Section~\ref{sec:identifiers}.)
An application identifier can be considered as the address of an application and has the following standard symbolic
representation:
\begin{verbatim}
<application-id> ::= <decimal-prefix-code>
<decimal-prefix-code> ::= <dec-num>"."<decimal-prefix-code> | <dec-num>
\end{verbatim}
where \texttt{<dec-num>} is a normal decimal number between $0$ and $255$.

@@

\begin{itemize}
    \item Installation of new Argennon applications and determining the update policy of a smart
    contract: if the contract is updatable or not, which accounts or smart contracts can update or uninstall
    the contract, and so on.
    \item Removing an Argennon application (if allowed).
    \item Updating an Argennon application (if allowed).
\end{itemize}

@@

Argennon accounts are entities defined inside the ARG application.
Every Argennon account is uniquely identified by a prefix code generated using \emph{accounts} prefix
tree. (See Section~\ref{sec:identifiers}) An account
identifier can be considered as the address of an account and has the following standard symbolic representation:
\begin{verbatim}
<account-id> ::= "0x"<hex-num>
\end{verbatim}
where \texttt{<hex-num>} is a hexadecimal number, using lower case
letters \texttt{[a-f]} for showing digits greater than $9$.

For example \texttt{0x24ffda}, \texttt{0x0} and \texttt{0x03a0000}, are valid standard symbolic
representations of account addresses.

A new account can be created by sending a proper HTTP request to the ARG smart contract. For creating
a new account two public keys need to be provided by the caller and registered in the Argennon smart contract.
One public key will be used for issuing digital signatures, and the other one will be used for voting. The
provided public keys need to meet certain cryptographic requirements,\footnote{Argennon uses Prove
Knowledge of the Secret Key (KOSK) scheme.} and can not be already registered in the system.

@@

\section{Transactions}\label{sec:transactions}
\emph{subsection is outdated and needs updating!}

@@

\subsection{Resource Declaration}\label{subsec:resource-declaration}
\emph{subsection is outdated and needs updating!}

@@

\begin{lstlisting}[language=python, frame=TB, float, title=An Argennon transaction in YAML format,
    label={lst:txn-example}]
---
fee: |
    PUT /balances/0x73.0xa2?to=fee&amount=0.26&sig=5b73CbmwQNRC7fWUY15 HTTP/1.1
call: |
    POST bttp://dapp.argennon.net/54.189.21/proposals HTTP/1.1
    Content-Type: application/json; charset=utf-8
    Content-Length: 77

### 2022-04-01 tex/sections/persistence.tex
Update some parts of `elements.tex`
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

The Argennon Smart Contract Execution Environment has two persistent memory areas: \emph{code area}, and \emph{heap}.
Code area stores the Argennon Standard Representation of
applications\footnote{also it stores applications' constants.}, and heap stores heap chunks.
Both of these data elements, ASRs and chunks, can be considered as continuous arrays of bytes.
Throughout this chapter, we shall call these data elements \emph{objects}.

@@

Pages of the AscEE storage are persisted using \emph{dynamic cryptographic accumulators}. Argennon
has three dynamic cryptographic accumulators: \emph{staking} database, which stores all the data that is associated with
the Argennon consensus protocol. \emph{code} database, which stores the AscEE code area, and \emph{heap} database,
which stores the AscEE heap. The commitment of these three accumulators are included in every block of the Argennon
blockchain. These accumulators, in the Argennon network, are hosted on special database nodes called Publicly
Verifiable Data Base (PV-DB) servers.
We consider the following properties for a PV-DB:
\begin{itemize}
    \item The PV-DB contains a mapping from a set of keys to a set of values.
    \item Every state of the database has a commitment \(C\).
    \item The PV-DB has a method \((D, \pi) = \text{get}(x)\), where \(x\) is a key and \(D\) is the associated data
    with \(x\), and \(\pi\) is a proof.
    \item A user having \(C\) and \(\pi\) can verify that \(D\) is really associated with \(x\), and \(D\) is not
    altered. Consequently, a user who can obtain \(C\) from a trusted source does not need to trust the PV-DB\@.
    \item Having \(\pi\) and \(C\) a user can compute the commitment \(C'\) for the database in which \(D'\) is
    associated with \(x\) instead of \(D\).
\end{itemize}

>>>>

The Argennon Smart Contract Execution Environment has two persistent memory areas: \emph{code area}, and \emph{heap}.
Code area stores the Argennon Standard Representation of
applications\footnote{also it stores applications' constants.}, and heap stores heap chunks.
Both of these data elements, ASRs and heap chunks, can be considered as continuous arrays of bytes.
Throughout this chapter, we shall call these data elements \emph{objects}.

@@

Pages of the AscEE storage are persisted using \emph{dynamic cryptographic accumulators}. Argennon
has three dynamic cryptographic accumulators: \emph{staking} database, which stores all the data that is associated with
the Argennon consensus protocol. \emph{code} database, which stores the AscEE code area, and \emph{heap} database,
which stores the AscEE heap. The commitment of these three accumulators are included in every block of the Argennon
blockchain. These accumulators, in the Argennon network, are hosted on special database nodes called Publicly
Verifiable Database (PV-DB) servers.
We consider the following properties for a PV-DB:
\begin{itemize}
    \item The PV-DB contains a mapping from a set of keys to a set of values.
    \item Every state of the database has a commitment \(C\).
    \item The PV-DB has a method \((D, \pi) = \text{get}(x)\), where \(x\) is a key and \(D\) is the associated data
    with \(x\), and \(\pi\) is a proof.
    \item A user having \(C\) and \(\pi\) can verify that \(D\) is really associated with \(x\), and \(D\) is not
    altered. Consequently, a user who can obtain \(C\) from a trusted source does not need to trust the PV-DB\@.
    \item Having \(\pi\) and \(C\) a user can compute the commitment \(C'\) for the database in which \(D'\) is
    associated with \(x\) instead of \(D\).
\end{itemize}
